---
name: Brandon Monier
address: "Institute for Genomic Diversity,\\tabularnewline Cornell University, Ithaca, New York"
www: btmonier.github.io
phone: +1 712-461-2851
email: "brandon.monier@gmail.com"
twitter: btmonier
github: btmonier
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
header_includes:
    - \ExecuteBibliographyOptions{useprefix=true}
    - renewcommand{\bibfont}{\normalfont\fontsize{10}{12.4}\sffamily}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(RefManageR)
library(scholar)
library(tidyverse)
library(vitae)
```

# Professional Experience
\begin{tabular}{rll}
    2018 - present & \textbf{Postdoctoral Researcher} in Dr. Ed Buckler's laboratory \\
                   & School of Integrated Plant Sciences, Cornell University
\end{tabular}

\hfill

# Education
\begin{tabular}{rll}
    2018 & \textbf{Ph.D.} & \textbf{Department of Biology and Microbiology} \\
         &                & South Dakota State University \\
         &                & \textit{Supervisors}: Drs. Heike B{\"u}cking and Jose Gonzalez-Hernandez \\[8pt]
    2013 & \textbf{M.S.}  & \textbf{Department of Agronomy, Horticulture and Plant Science} \\
         &                & South Dakota State University \\
         &                & \textit{Supervisor}: Dr. Jose Gonzalez-Hernandez \\[8pt]
    2008 & \textbf{B.S.}  & \textbf{Microbiology} \\
         &                & South Dakota State Univeristy \\
\end{tabular}

\hfill

# Technologies
R/Shiny, Python, Perl, bash/shell, C/C++, Neo4J/Cypher, markup languages including \LaTeX,
R Markdown, HTML, CSS, and some superficial knowledge of JavaScript, and Java.

\hfill

# Publications

```{r in_prep}
bibliography_entries("btmonier_pubs.bib", title = "Research Papers (in preparation)") %>%
    filter(grepl(pattern = "\\\\noop", x = year))
```

```{r research_papers}
bibliography_entries("btmonier_pubs.bib", title = "Research Papers", sorting = "ydnt") %>%
    filter(!grepl(pattern = "\\\\noop", x = year)) %>%
    filter(bibtype == "Article") %>%
    arrange(desc(year), author)
```

```{r book_chapters}
bibliography_entries("btmonier_pubs.bib", title = "Book Chapters") %>%
    filter(bibtype %in% c("InBook")) %>%
    arrange(year)
```

```{r phd_thesis}
bibliography_entries("btmonier_pubs.bib", title = "PhD Thesis") %>%
    filter(bibtype == "PhdThesis")
```

```{r ms_thesis}
bibliography_entries("btmonier_pubs.bib", title = "Master's Thesis") %>%
    filter(bibtype == "MastersThesis")
```

\hfill

# Teaching Experience
\begin{tabular}{rll}
    2018        & \textbf{Teaching Assistant} & BOT-327L, Plant Physiology \\
                &                             & South Dakota State University \\
    2016        & \textbf{Teaching Assistant} & BIOL-153L, General Biology II \\
                &                             & South Dakota State University \\
    2015        & \textbf{Teaching Assistant} & BOT-201L, General Botany \\
                &                             & South Dakota State University \\
    2014 - 2017 & \textbf{Teaching Assistant} & BIOL-151L, General Biology I \\
                &                             & South Dakota State University \\
    2011        & \textbf{Teaching Assistnat} & PS-333L, Diseases of Field Crops \\
                &                             & South Dakota State University \\
\end{tabular}

\hfill

# Mentoring Experience
* \textit{April DeMell}, undergraduate (3 months, full-time), South Dakota State University, 2016
* \textit{Clarissa Mercado}, undergraduate (3 months, full-time), South Dakota State University, 2016
* \textit{Jerry Cordero Sepulv{\'e}da}, undergraduate (3 months, full-time) South Dakota State University, 2015
* \textit{Winly Mai}, undergraduate (3 months, full-time), South Dakota State University, 2015
* \textit{Merritt Burch}, undergraduate (3 months, full-time), South Dakota State University, 2014
* \textit{Vincent Peta}, undergraduate (~9 months, part-time), South Dakota State University, 2013-2014
* \textit{Sabrina Bushlack}, undergraduate (3 months, full-time), South Dakota State University, 2013
* \textit{Linh Anh Cat}, undergraduate (3 months, full-time), South Dakota State University, 2013

