---
name: Brandon Monier
address: "School of Integrated Plant Sciences,\\tabularnewline Cornell University, Ithaca, New York"
www: btmonier.github.io
phone: +1 712-461-2851
email: "brandon.monier@gmail.com"
twitter: btmonier
github: btmonier
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
header_includes:
    - \ExecuteBibliographyOptions{useprefix=true}
    - renewcommand{\bibfont}{\normalfont\fontsize{10}{12.4}\sffamily}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(RefManageR)
library(scholar)
library(tidyverse)
library(vitae)
```

# Professional Experience
\begin{tabular}{rll}
    2018 - present & \textbf{Postdoctoral Researcher} in Dr. Ed Buckler's laboratory \\
                   & School of Integrated Plant Sciences, Cornell University
\end{tabular}

\hfill

# Education
\begin{tabular}{rll}
    2018 & \textbf{Ph.D.} & \textbf{Department of Biology and Microbiology} \\
         &                & South Dakota State University \\
         &                & \textit{Supervisors}: Drs. Heike B{\"u}cking and Jose Gonzalez-Hernandez \\[8pt]
    2013 & \textbf{M.S.}  & \textbf{Department of Agronomy, Horticulture and Plant Science} \\
         &                & South Dakota State University \\
         &                & \textit{Supervisor}: Dr. Jose Gonzalez-Hernandez \\[8pt]
    2008 & \textbf{B.S.}  & \textbf{Microbiology} \\
         &                & South Dakota State Univeristy \\
\end{tabular}

\hfill

# Programming Languages
R, Python, Perl, bash/shell, C/C++, markup languages including \LaTeX,
R Markdown, HTML, CSS, and some superficial knowledge of JavaScript, and Java.

\hfill

# Publications

```{r in_prep}
bibliography_entries("btmonier_pubs.bib", title = "Research Papers (in preparation)") %>%
    filter(grepl(pattern = "btm_pre", x = key))
```

```{r research_papers}
bibliography_entries("btmonier_pubs.bib", title = "Research Papers") %>%
  filter(bibtype == "Article") %>%
  arrange(year, author)
```

```{r book_chapters}
bibliography_entries("btmonier_pubs.bib", title = "Book Chapters") %>%
  filter(bibtype %in% c("InBook")) %>%
  arrange(year, author)
```

```{r phd_thesis}
bibliography_entries("btmonier_pubs.bib", title = "PhD Thesis") %>%
    filter(bibtype == "PhdThesis")
```

```{r ms_thesis}
bibliography_entries("btmonier_pubs.bib", title = "Master's Thesis") %>%
    filter(bibtype == "MastersThesis")
```

\hfill

# Teaching and Mentoring Experience
\begin{tabular}{rll}
    2018 & \textbf{Teaching Assistant} \\
         & BOT-327L, Plant Physiology \\
         & South Dakota State University \\
    2016 & \textbf{Teaching Assistant} \\
         & BIOL-153L, General Biology II \\
         & South Dakota State University \\

\end{tabular}
